Package corpus

### 2020-05-09 evaluation/R/package-corpus.Rmd
Update corpus analysis - revdeps, roxygen, renaming

create_tags(path(TAGS_DIR, "package-corpus.tex"), prefix="PC", default=TRUE)
```

@@

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") 
```

@@

    r(paste(prefix, "runtime"), as.duration(sum(df$runnable_time, na.rm=T))),
    r(paste(prefix, "mean runtime"), as.duration(mean(df$runnable_time, na.rm=T))),
    r(paste(prefix, "median runtime"), as.duration(median(df$runnable_time, na.rm=T)))
  )
}

@@

```{r list of reverse depenencies}
corpus_revdeps <- pkgs_revdeps_raw %>% semi_join(corpus, by="package") %>% distinct(revdep)
write_lines(corpus_revdeps, CORPUS_REVDEPS)
```

>>>>

create_tags(path(TAGS_DIR, "package-corpus.tex"), prefix="", default=TRUE)
```

@@

### Package roxygen

```{r}
pkgs_roxygen <-
  read_csv(
    PACKAGE_USES_ROXYGEN,
    col_types=cols(
      package = col_character(),
      uses_roxygen = col_logical()
    )
  )
```

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```

@@

    r(paste(prefix, "runtime"), as.duration(sum(df$runnable_time, na.rm=T))),
    r(paste(prefix, "mean runtime"), as.duration(mean(df$runnable_time, na.rm=T))),
    r(paste(prefix, "median runtime"), as.duration(median(df$runnable_time, na.rm=T))),

    r(paste(prefix, "using roxygen"), sum(df$uses_roxygen, na.rm=T))
  )
}

@@

```{r list of reverse depenencies}
corpus_revdeps <- pkgs_revdeps_raw %>% semi_join(corpus, by="package")
write_csv(corpus_revdeps, CORPUS_REVDEPS)
write_lines(unique(corpus_revdeps$revdep), CORPUS_REVDEPS_UNIQUE)
```
